Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-23 manuscript.Rmd
Updated stacked area chart.

ebp.df <- abstract.df[grep("evidence\\s?based\\spractices?|ebp|empirically\\s?supported\\streatments?", abstract.df$abstract), ]
ebp.df$ebp <- rep("ebp", nrow(ebp.df))

meta.df <- abstract.df[grep("meta\\s?analysis", abstract.df$abstract), ]
meta.df$meta <- rep("meta", nrow(meta.df))

rct.df <- abstract.df[grep("randomi[s|z]ed.*trial|[^non]experimental\\sdesign|rct|controlled\\sclinical\\strial|cct", abstract.df$abstract), ]
rct.df$rct <- rep("rct", nrow(rct.df))

systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
systematicReview.df$systematicReview <- rep("sr", nrow(systematicReview.df))

practiceGuidelines.df <- abstract.df[grep("practice\\sguidelines|treatment\\sguidelines?", abstract.df$abstract), ]
practiceGuidelines.df$practiceGuidelines <- rep("pg", nrow(practiceGuidelines.df))

quasi <- abstract.df[grep("quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
quasi.df$quasi <- rep("quasi", nrow(quasi.df))

longitudinal.df <- abstract.df[grep("longitudinal\\sstudy", abstract.df$abstract), ]
longitudinal.df$longitudinal <- rep("longitudinal", nrow(longitudinal.df))

observational.df <- abstract.df[grep("cohort\\sstudy|case\\scontrol\\sstudy", abstract.df$abstract), ]
observational.df$observational <- rep("observational", nrow(observational.df))

literatureReview.df <- abstract.df[grep("literature\\sreview|review of the.*literature", abstract.df$abstract),]
literatureReview.df$literatureReview <- rep("literatureReview", nrow(literatureReview.df))

survey.df <- abstract.df[grep("survey", abstract.df$abstract), ]
survey.df$survey <- rep("survey", nrow(survey.df))

>>>>

ebp.df <- abstract.df[grep("evidence\\s?based\\spractices?|ebp|empirically\\s?supported\\streatments?", abstract.df$abstract), ]
ebp.df$studyType <- rep("ebp", nrow(ebp.df))

meta.df <- abstract.df[grep("meta\\s?analysis", abstract.df$abstract), ]
meta.df$studyType <- rep("meta", nrow(meta.df))

rct.df <- abstract.df[grep("randomi[s|z]ed.*trial|[^non]experimental\\sdesign|rct|controlled\\sclinical\\strial|cct", abstract.df$abstract), ]
rct.df$studyType <- rep("rct", nrow(rct.df))

systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
systematicReview.df$studyType <- rep("sr", nrow(systematicReview.df))

practiceGuidelines.df <- abstract.df[grep("practice\\sguidelines|treatment\\sguidelines?", abstract.df$abstract), ]
practiceGuidelines.df$studyType <- rep("pg", nrow(practiceGuidelines.df))

quasi.df <- abstract.df[grep("quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
quasi.df$studyType <- rep("quasi", nrow(quasi.df))

longitudinal.df <- abstract.df[grep("longitudinal\\sstudy", abstract.df$abstract), ]
longitudinal.df$studyType <- rep("longitudinal", nrow(longitudinal.df))

observational.df <- abstract.df[grep("cohort\\sstudy|case\\scontrol\\sstudy", abstract.df$abstract), ]
observational.df$studyType <- rep("observational", nrow(observational.df))

literatureReview.df <- abstract.df[grep("literature\\sreview|review of the.*literature", abstract.df$abstract),]
literatureReview.df$studyType <- rep("literatureReview", nrow(literatureReview.df))

survey.df <- abstract.df[grep("survey", abstract.df$abstract), ]
survey.df$studyType <- rep("survey", nrow(survey.df))

evidence.df <- rbind(ebp.df, meta.df, rct.df, systematicReview.df, 
     practiceGuidelines.df, quasi.df, longitudinal.df, observational.df, 
     literatureReview.df, survey.df)

evidence.summary <- select(evidence.df, -abstract) %>% 
    group_by(year, studyType) %>%
    summarize(N = n()) %>%
    group_by(studyType) %>%
  mutate(cumulative = cumsum(N))

evidence.summary.main <- filter(evidence.summary, studyType != "literatureReview" , studyType != "survey" ,
    studyType != "ebp" , studyType != "longitudinal", studyType != "pg", studyType != "quasi")

cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
evidence.summary.main <- ungroup(evidence.summary.main)
evidence.summary.main$year <- as.numeric(evidence.summary.main$year)
evidence.summary.main$studyType <- as.factor(evidence.summary.main$studyType)

year.labs <- as.character(seq(1989,2013, 2))

ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary.main)), 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.80, colour = "black", size = .2) + 
    scale_fill_manual(values=cp, 
          breaks = rev(levels(evidence.summary.main$studyType)),
            labels = c("Systematic review", "RCT", 
            "Cohort/Case Control", "Meta-analysis")) +
  ylim(c(0, 60)) + 
    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1), 
          panel.grid.minor=element_blank(),
         legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Frequency") + 
    xlab("Year") + 
    labs(fill = "Study type") + 
    scale_y_continuous(breaks = seq(0,60, 10))
